\documentclass[10pt,conference]{IEEEtran}

\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{xspace}
\usepackage{multirow}
\usepackage{subcaption}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

 \newcommand{\evpi}{EVPI\xspace}

\begin{document}

\title{Automatically Selecting Follow-up Questions for Deficient Bug Reports}

\author{\IEEEauthorblockN{Mia Mohammad Imran}
\IEEEauthorblockA{\textit{Virginia Commonwealth University}\\
Richmond, Virginia, U.S.A. \\
imranm3@vcu.edu}
\and
\IEEEauthorblockN{Agnieszka Ciborowska}
\IEEEauthorblockA{\textit{Virginia Commonwealth University} \\
Richmond, Virginia, U.S.A. \\
ciborowskaa@vcu.edu}
\and
\IEEEauthorblockN{Kostadin Damevski}
\IEEEauthorblockA{\textit{Virginia Commonwealth University} \\
Richmond, Virginia, U.S.A. \\
kdamevski@vcu.edu}
}

\maketitle

\begin{abstract}
% quality bug reporting is important
The availability of quality information in bug reports that are created daily by software users is key
to rapidly fixing software faults.
%
% Despite the success of efforts to make bug reporting consistent and detailed, numerous bug reports still lack
% sufficient important information.
%
Improving incomplete or deficient bug reports, which are numerous in many popular and actively developed open source software projects, can make software maintenance more effective and improve software quality.
%
In this paper, we propose a system that addresses the problem of bug report incompleteness by automatically posing follow-up questions, intended to elicit answers that add value and provide missing information to a bug report.
%
Our system is based on selecting follow-up questions from a large corpus of already posted follow-up questions on GitHub.
%
% To find adequate follow-up questions we use a combination of information retrieval and deep neural networks.
% %
% Using information retrieval we retrieve a candidate set of follow-up questions, while neural networks is responsible for estimating the improvement in the quality of a bug report when an answer for a follow-up question is provided.
%
To retrieve the best follow-up question for a specific deficient bug report we estimate the similarity between the text of the two bug reports, i.e., the similarity between a bug report corresponding to a candidate follow-up question and the deficient bug report. We combine this with an estimate of the utility the expected answer to the follow-up question would provide to the deficient bug report.
%
Evaluation of our system, based on a manually annotated held out data set, indicates improved
performance over a set of simple and ablation baselines.
%
A survey of software developers confirms the held-out set evaluation result that about half of the selected follow-up questions are considered valid. The developer survey also indicates that the valid follow-up questions are useful and can provide new information to a bug report most of the time and are specific to a bug report some of the time.

\end{abstract}

\begin{IEEEkeywords}
follow-up questions, bug reporting, bug triage
\end{IEEEkeywords}

\input{intro}

\input{motivation}

\input{model}

\input{evaluation}

\input{related}

\section{Conclusions and Future Work}

\section*{Acknowledgment}
%The authors acknowledge the help of Sudeep Dharanikota in implementing some of the bug report patterns. This material is based upon work supported by the National Science Foundation under Grant No. (NSF grant number)
Coming soon.

\bibliographystyle{IEEEtran}
\bibliography{paper}

\end{document}
